Articles

### 2016-12-31 articles/articles.Rmd
license badge

---
title: "Articles"
date: "`r Sys.Date()`"
author: "Ming-Yu Liu"
output:
  rmdformats::readthedown:
    highlight: pygments
---

@@

>>>>

---
title: "Articles"
date: "`r Sys.Date()`"
author: "Ethen Liu"
output:
  rmdformats::readthedown:
    highlight: pygments
---

@@

- 2016.12.29 | Data Science Newsletter list. [[Medium](https://medium.com/blend-your-data/a-four-minute-read-big-data-and-data-science-newsletter-list-to-get-you-informed-on-anything-data-669d8e2c4b09#.2lukcelgg)]
